RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-01 manuscripts/manuscript.Rmd
Removes reminder of previous structure.
Fixes and edits to custom metadata intro.

NeXML uses the "Resource Description Framework in Annotations" (RDFa),
as described in @Vos_2012 or @W3C_2014, to encode metadata
annotations. This standard provides a precisely specified,
machine-readable format that maintains backwards compatibility with
compliant NeXML parsers (and thus `RNeXML`), because the capacity of a
tool to _parse_ annotations is not predicated on _understanding_
annotations it has not seen before.

@@

- Automatic annotation: 
- Adding common metadata fields (`add_basic_metadata`)
- Taxonomic identifiers (`taxize_nexml`)
- Generic metadata (`add_meta`)
- Extending the NeXML standard using RDFa

@@

The `RNeXML` methods described above for built-in metadata annotations
perform this cast automatically behind the scenes, including mapping
metadata attributes to terms in requisite common vocabularies (such as
Dublin Core for "title", "creator", etc.) or ontologies. Giving
metadata properties (and sometimes values) as vocabulary or ontology
terms rather than simple text strings is crucial for allowing machines
to not only parse but also interpret their semantics. To achieve this
benefit for custom metadata extensions, the user necessarily needs to
handle certain technical details from which the `RNeXML` API shields
her otherwise, in particular the vocabularies or ontologies of
metadata terms in the form of globally unique identifiers (normally
HTTP URIs). To be consistent with XML terminology for more technical
users, `RNeXML` calls these _namespaces_, and their abbreviations
_prefixes_. For example, the namespace for the Dublin Core Metadata
Terms vocabulary, commonly abbreviated with "dc", is
"http://purl.org/dc/elements/1.1/". Using its abbreviation, a metadata
property "dc:title" expands to the identifier
"http://purl.org/dc/elements/1.1/title", the identifier for the term
"title" in said vocabulary.

`RNeXML` includes methods to obtain and manipulate these values. The
`get_namespaces()` method accepts a `nexml` object and returns a list
with element names being the namespace abbreviations and element
values being the corresponding identifies (typically HTTP URIs):

>>>>

NeXML uses the "Resource Description Framework in Annotations" (RDFa),
as described in @Vos_2012 or @W3C_2014, to encode metadata
annotations. This standard provides a precisely specified,
machine-readable format that maintains backwards compatibility with
compliant NeXML parsers (and thus `RNeXML`), because the capacity of a
tool to _parse_ annotations is not predicated on _understanding_
the meaning of annotations it has not seen before.

@@

@@

The `RNeXML` methods described above for built-in metadata annotations
perform this cast automatically behind the scenes, including mapping
metadata attributes to terms in requisite common vocabularies (such as
Dublin Core for "title", "creator", etc.) or ontologies. Giving
metadata properties (and sometimes values) as vocabulary or ontology
terms rather than simple text strings is crucial for allowing machines
to not only parse but also interpret and potentially reason over their
semantics. To achieve this benefit for custom metadata extensions, the
user necessarily needs to handle certain technical details from which
the `RNeXML` API shields her otherwise, in particular the vocabularies
or ontologies of metadata terms in the form of globally unique
identifiers (normally HTTP URIs). To be consistent with XML
terminology for more technical users, `RNeXML` calls these
_namespaces_, and their abbreviations _prefixes_. For example, the
namespace for the Dublin Core Metadata Terms vocabulary, commonly
abbreviated with "dc", is "http://purl.org/dc/elements/1.1/". Using
its abbreviation, a metadata property "dc:title" expands to the
identifier "http://purl.org/dc/elements/1.1/title", the identifier for
the term "title" in said vocabulary. When resolved as a HTTP URI, the
identifier resolves to a human and machine-readable
(depending on how the identifier is resolved) definition of precisely
what the term `title` in Dublin Core means. In contrast, just using
the text string "title" could also mean the title of a person, a legal title, the verb title, etc.  Although URI identifiers of metadata
vocabularies and terms are not required to resolve, for machines to
derive the maximum benefit from them, they should resolve to RDF
statements defining their semantics.

`RNeXML` includes methods to obtain and manipulate metadata
properties, values, identifiers, and namespaces. The
`get_namespaces()` method accepts a `nexml` object and returns a list
with element names being the namespace abbreviations and element
values being the corresponding identifiers (typically HTTP URIs) for
all annotations attached to the object or one of the contained data elements:
